Nonparametric Goodness-of-Fit Tests for Discrete Null Distributions

### 2010-11-18 rjournal/RJtemplate.tex
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/ks-test@31 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

While we have implemented the two most popular variants of 
goodness-of-fit tests for discrete distributions, further 
generalizations of tests are described in the
extended study of \cite{dewev1973}.  We also provide general one-sample
Cram\'{e}r-von Mises testing for continuous distributions simply
to help complement the abilities provided by several other
R packages, although these tests are not the focus of this paper.
In particular, functions implemented in package \pkg{nortest} focus on the
composite hypothesis of normality, while
package \pkg{ADGofTest} provides the Anderson-Darling variant
of the test for continuous distributions.  Packages
\pkg{CvM2SL1Test} and \pkg{CvM2SL1Test} provide support for
two-sample Cram\'{e}r-von Mises tests with continuous distributions.
 *** Need to be added
to the bibliography. ***

>>>>

While we have implemented the two most popular variants of 
goodness-of-fit tests for discrete distributions, further 
generalizations of tests are described in the
extended study of \cite{dewev1973}.  We also provide general one-sample
Cram\'{e}r-von Mises testing for continuous distributions simply
to help complement the abilities provided by several other
R packages, although these tests are not the focus of this paper.
In particular, functions implemented in package \pkg{nortest} focus on the
composite hypothesis of normality, while
package \pkg{ADGofTest} provides the Anderson-Darling variant
of the test for continuous distributions.  Packages
\pkg{CvM2SL1Test} and \pkg{CvM2SL1Test} provide support for
two-sample Cram\'{e}r-von Mises tests with continuous distributions.
Package \pkg{cramer} offers a multivariate Cram\'{e}r test for
the two-sample problem.  Possible reference, though it isn't clear
if this particular one is really part of this literature segment?
\url{http://en.scientificcommons.org/39157548}

 *** Need to be added
to the bibliography, whatever we choose to do ***
